Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-31 automatica/paper.tex
responses

In the second stage, 
the automated synthesis process starts with Step~A, where the
\tool~translates the model specification into an ANSI-C program.  
In Step~B, the discussed CEGIS engine is invoked, 
in order to synthesize the digital controller w.r.t.~the specification given on the model.  
Finally, in Step~C, the synthesized digital controller is generated.  
The output of \tool~is the synthesized digital controller \note{you mean: the closed-loop model}, 
which is represented either as a transfer function or in state-space form (in this article we consider the latter case).  
The synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized with respect to the effects of finite-precision arithmetic; 
otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
then the synthesis is considered to have \emph{failed}.

@@

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts \note{above: failures} are indicated by~\xmark.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.

>>>>

In the second stage, 
the automated synthesis process starts with Step~A, where the
\tool~translates the model specification into an ANSI-C program.  
In Step~B, the discussed CEGIS engine is invoked, 
in order to synthesize the digital controller w.r.t.~the specification given on the model.  
Finally, in Step~C, the synthesized digital controller is generated.  
The output of \tool~is the closed-loop model with the synthesized digital controller, 
which is represented either as a transfer function or in state-space form (in this article we consider the latter case).  
The synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized with respect to the effects of finite-precision arithmetic; 
otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
then the synthesis is considered to have \emph{failed}.

@@

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts \note{above: failures. No, these are timeouts. I can't find any mention of failures} are indicated by~\xmark.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.
